Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-12 Draft.tex
edit abstract

Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature. This is called the critical temperature. We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$ to be $xx \pm yy \textrm{ K}$ and $uu \pm vv \textrm{ K}$\textcolor{magenta}{ respectively}, by measuring the voltage across the resistor as a function of temperature. \textcolor{red}{This reads as if you just measured the voltage, without passing any current. That would be a measurement of thermoelectric voltage, as with a thermocouple. You actually determined the critical temperature by passing a known current through the sample, measured the resulting voltage drop across the sample to find the resistance, then looked to see when the resistance became zero. Or reached the halfway point in the transition to zero. or some other criteria. }

@@

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$, where $n=1,2,\textrm{ or },3$. %n=3 mainly for colorado superconductor 110 Tc
The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$, the critical temperature depends on the value of n.  
They are 20 K, 85 K, and 110 K, for $n=1,2,\textrm{ and }3$, respectively.\cite{temps}

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
We used different methods to measure the critical temperature of the two superconductors. 
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current provides a more accurate reading of the voltage across the sample, because it removes any offset the voltmeter may have.
The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. 
The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
 \textcolor{blue}{Include circuit diagrams.}

@@

We placed the superconductor inside a styrofoam cup filled with sand. 
The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points. 
We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup. We waited for the superconductor to settle to a minimum temperature. Then we recorded $V_{\textrm{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.

We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions. Since changes in $V_{BSCCO}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.  
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.

@@

First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig. \ref{TCplot}). While it was best fit piecemeal, a single curve was able to cover our temperature range, and we used that function to convert our thermocouple voltages in later fits.

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} , with fit lines across different sections.}
\label{TCplot}
\end{figure}

@@

\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \textrm{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K? If the latter, what do you take to be the uncertainty in your determination of that midpoint? Also, you mention two trials, but only show one. Finally, why 4 sig figs for the critical temperature, if your uncertainty is on the order of 0.5 to 4.5 K, depending on how you define it. } 
\textcolor{blue}{That said, I like the method used to find the 1/2 way point (by drawing a line with 1/2 the slope seen in the resistive state). If you don't yet have a criteria for uncertainty for that value, one common definition is from 10 percent to 90 percent. So you could plot lines with slopes that are 10 percent and 90 percent to find those boundry points.}

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of \textcolor{red}{fix this:} 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K. According to the \textcolor{red}{Teachspin} manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\textrm{Bi}_{2,1}\textrm{Sr}_{n+1}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \textcolor{blue}{what is your source for this information about Tc values for n  = 1, 2, and 3?} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.

@@

\bibitem{ybcotemp} R. J. Cava, B. Batlogg, R. B. van Dover, D. W. Murphy, S. Sunshine, T. Siegrist, J. P. Remeika, E. A. Rietman, S. Zahurak, and G. P. Espinosa, "Bulk superconductivity at 91 K in sngle-phase oxygen-deficient perovskite $\textrm{Ba}_2\textrm{YCU}_3\textrm{O}_{9-\delta}$, Phys. Rev. Letters 58, 1676 (1987).

\bibitem{temps} J. M. Tarascon, W. R. McKinnon, P. Barboux, D. M. Hwang, B. G. Bagley, L. H. Greene, G. W. Hull, Y. LePage, N. Stoffel, and M. Giroud, "Preparation, structure, and properties of the superconducting compound series $\textrm{Bi}_2\textrm{Sr}_2\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_y$ with $n=1,2,\textrm{ and }3$", Phys. Rev. B 38, 8885 (1998).

>>>>

Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature. This is called the critical temperature. We determine the critical temperatures to be $xx \pm yy \text{ K}$ and $xx \pm yy \text{ K}$ for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$.
We find a single phase transition at $110\pm vv \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$.
The critical temperatures are found by passing a fixed current through the superconducting sample and measuring the change in voltage across the sample to determine its resistance. 
We give the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. Previous measurement of the critical temperature for YBCO give a critical temperature of 91 K. Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature.    
This confirms that our BSCCO consists of mainly $n=3$ as it was stated it the manual that came with our samples.

@@

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
In our experiment, we look at two high temperature superconductors, $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ and $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, where $n=1,2,\text{ or },3$. %n=3 mainly for colorado superconductor 110 Tc
The amount of oxygen in $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
For $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, the critical temperature depends on the value of n.  
They are 20 K, 85 K, and 110 K, for $n=1,2,\text{ and }3$, respectively.\cite{temps}

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. The manual from Colorado Superconductor Inc. notes that the BSCCO samples consists of mainly $n=3$. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
We used different methods to measure the critical temperature of the two superconductors. 
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current provides a more accurate reading of the voltage across the sample, because it removes any offset the voltmeter may have.
The voltage across the YBCO sample, $V_{\text{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. 
The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
 \textcolor{blue}{Include circuit diagrams.}

@@

We placed the superconductor inside a styrofoam cup filled with sand. 
The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points. 
We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup. We waited for the superconductor to settle to a minimum temperature. Then we recorded $V_{\text{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.

We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions. Since changes in $V_{\text{BSCCO}}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.  
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.

@@

First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the Colorado Superconductor Inc. experiment manual that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig. \ref{TCplot}). While it was best fit piecemeal, a single curve was able to cover our temperature range, and we used that function to convert our thermocouple voltages in later fits.

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the Colorado Superconductor Inc experiment manual, with fit lines across different sections.}
\label{TCplot}
\end{figure}

@@

\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \text{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K? If the latter, what do you take to be the uncertainty in your determination of that midpoint? Also, you mention two trials, but only show one. Finally, why 4 sig figs for the critical temperature, if your uncertainty is on the order of 0.5 to 4.5 K, depending on how you define it. } 
\textcolor{blue}{That said, I like the method used to find the 1/2 way point (by drawing a line with 1/2 the slope seen in the resistive state). If you don't yet have a criteria for uncertainty for that value, one common definition is from 10 percent to 90 percent. So you could plot lines with slopes that are 10 percent and 90 percent to find those boundry points.}

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of \textcolor{red}{fix this:} 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K. According to the \textcolor{red}{Teachspin} manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \textcolor{blue}{what is your source for this information about Tc values for n  = 1, 2, and 3?} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.

@@

\bibitem{ybcotemp} R. J. Cava, B. Batlogg, R. B. van Dover, D. W. Murphy, S. Sunshine, T. Siegrist, J. P. Remeika, E. A. Rietman, S. Zahurak, and G. P. Espinosa, "Bulk superconductivity at 91 K in sngle-phase oxygen-deficient perovskite $\text{Ba}_2\text{YCU}_3\text{O}_{9-\delta}$, Phys. Rev. Letters 58, 1676 (1987).

\bibitem{temps} J. M. Tarascon, W. R. McKinnon, P. Barboux, D. M. Hwang, B. G. Bagley, L. H. Greene, G. W. Hull, Y. LePage, N. Stoffel, and M. Giroud, "Preparation, structure, and properties of the superconducting compound series $\text{Bi}_2\text{Sr}_2\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_y$ with $n=1,2,\text{ and }3$", Phys. Rev. B 38, 8885 (1998).
